Preregistration for modelling in ecolgy and conservation

### 2024-03-27 _analysis/EcoConsPreReg-supervisor_draft-Sep-2020.Rmd
reformat manuscript draft .rmd
- fix rel filepath to references.bib

---
title: "Preregistration for modelling in ecolgy and conservation"
description: |
  Working Draft.
author:
  - name: Elliot Gould 
    affiliation: School of BioSciences, University of Melbourne
  - name: Chris Jones
    affiliation: Department of Environment Land and Water
  - name: Libby Rumpff
    affiliation: School of BioSciences, University of Melbourne
  - name: Hannah Fraser
    affiliation: School of BioSciences, University of Melbourne
  - name: Fiona Fidler
    affiliation: School of BioSciences, University of Melbourne
abstract: "Blah blah"
date: "`r Sys.Date()`"
bibliography: ./data/references.bib
output: #
  distill::distill_article:
  self_contained: false
---

>>>>

---
title: "Preregistration for modelling in ecolgy and conservation"
description: |
  Working Draft.
author:
  - name: Elliot Gould 
    affiliation: School of BioSciences, University of Melbourne
  - name: Chris Jones
    affiliation: Department of Environment Land and Water
  - name: Libby Rumpff
    affiliation: School of BioSciences, University of Melbourne
  - name: Hannah Fraser
    affiliation: School of BioSciences, University of Melbourne
  - name: Fiona Fidler
    affiliation: School of BioSciences, University of Melbourne
abstract: "Blah blah"
date: "`r Sys.Date()`"
bibliography: ../data/references.bib
output: #
  distill::distill_article:
  self_contained: false
---
